---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: 'Helvetica Neue', sans-serif;
  line-height: 1.6;
  color: #333;
}

h2 {
  color: #2c3e50;
  border-bottom: 2px solid #3498db;
  padding-bottom: 0.3em;
}

.plot-title {
  text-align: center;
  color: #7f8c8d;
  margin: 20px 0;
}

.highlight {
  color: #e74c3c;
  font-weight: 600;
}
```

## What's going on with this data?

```{r}
# Part D: Data Exploration
# Load required packages
library(tidyverse)
library(lubridate)

# Import data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQkwClEkB_U3kQvzwhNwERT-uiQqZmempIP4ehI6cH99wZIDV3QGF8Jd-YfXB0rAsD6dMGXhZLNgbJd/pub?gid=997552583&single=true&output=csv") %>% 
  rename(
    genre = "1. Which music genre(s) do you listen to the most today?",
    duration = "2. Duration of listening in a day (in minutes)?",
    scenario = "3. In which scenario do you listen to music the most today?",
    date = "4. Date of Today?"
  ) %>% 
  mutate(
    date = dmy(date),
    weekday = wday(date, label = TRUE, week_start = 1),
    date_label = format(date, "%m/%d")  # Format date for plotting
  )

# Calculate summary statistics
genre_summary <- logged_data %>% 
  group_by(genre) %>% 
  summarise(
    avg_duration = round(mean(duration), 1),
    min_duration = round(min(duration), 1),
    max_duration = round(max(duration), 1),
    total_sessions = n()
  ) %>% 
  arrange(desc(avg_duration))

# Scenario distribution
scenario_counts <- logged_data %>% 
  count(scenario) %>% 
  mutate(percentage = round(n / sum(n) * 100, 1))

# Daily total duration
daily_summary <- logged_data %>%
  group_by(date_label) %>%
  summarise(total_duration = sum(duration))

# Generate visualizations
genre_plot <- ggplot(genre_summary, aes(x = reorder(genre, total_sessions), y = total_sessions)) +
  geom_col(fill = "#4E79A7") +
  geom_text(aes(label = total_sessions), hjust = -0.2, color = "darkblue") +
  labs(
    title = "Music Genre Frequency Distribution",
    x = "Genre",
    y = "Number of Sessions"
  ) +
  coord_flip() +
  theme_minimal()

# Scenario distribution
scenario_plot <- ggplot(scenario_counts, aes(x = reorder(scenario, percentage), y = percentage)) +
  geom_col(fill = "#E15759") +
  geom_text(aes(label = paste0(percentage, "%")), hjust = -0.2, color = "darkred") +
  labs(
    title = "Listening Scenario Distribution",
    x = "Scenario",
    y = "Percentage (%)"
  ) +
  coord_flip() +
  theme_minimal()

# Daily listening duration
daily_plot <- ggplot(daily_summary, aes(x = reorder(date_label, as.Date(date_label, "%m/%d")), y = total_duration)) +
  geom_bar(stat = "identity", fill = "#59A14F", width = 0.7) +
  geom_text(aes(label = total_duration), vjust = -0.5, color = "darkgreen") +
  labs(
    title = "Daily Total Listening Duration",
    x = "Date (MM/DD)",
    y = "Total Minutes"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display results
genre_plot
scenario_plot
daily_plot

# dynamic comment
dynamic_comment <- paste(
  "The favourite music genre is", genre_summary$genre[1],
  "with an average listening duration of", genre_summary$avg_duration[1], "minutes per session.",
  "The most common listening scenario is", scenario_counts$scenario[which.max(scenario_counts$n)],
  "which accounts for", max(scenario_counts$percentage), "% of total listening time."
)


```

## My data source:  
From March 10 2025 to March 30 2025, I collected music listening records from a music app. The dataset includes:  
- **Daily listening duration** (total minutes listened each day)  
- **Active time periods** (to analyze listening scenarios during different times of the day)  
- **Top artists by listening duration** (used to infer preferred music genres based on the most-listened artists)

I would like to explore the most-listened music genre by total playtime during the past 21 consecutive days.

## Dynamic comment:
`r dynamic_comment`